Contracts for Contracts

### 2023-07-09 paper/background.tex
background section [draft]

The above example demonstrates that addresses provide crucial features in Solidity, including:

\noindent
\textit{\underline{Access control}.} 
Addresses, when regarded as first-class values, play a pivotal role in enforcing access control within Solidity. 
They facilitate the restriction of privileged function invocations and the allocation of diverse permissions to individual users. 
Developers must carefully construct assertions based on numeric values associated with addresses to ensure the correctness of access control mechanisms.

\noindent
\textit{\underline{Flexible Interaction}.} 
Addresses can also be invoked and execute arbitrary computations. 
This capability empowers contracts to interact flexibly with other contracts, even if those contracts are deployed by third parties with undisclosed implementations. 
Consequently, the ecosystem of smart contracts can be incrementally developed in a decentralized manner, with various developers contributing through the deployment of their own contracts. 
Future developers can effortlessly interact with existing contracts by invoking their functions using addresses. 
Nonetheless, due to the possibility of adversarial actors developing and deploying their own contracts, curated security checks must be enforced when invoking higher-order functions up on addresses.

>>>>

This example demonstrates how addresses facilitate key features in Solidity, including:

\noindent
\textit{\underline{Access control}.}
Addresses, when treated as first-class values, play a crucial role in the implementation of access control in Solidity.
They enable the restriction of privileged function invocations and the assignment of diverse permissions to distinct users.
Developers are thus obligated to carefully design assertions based on the numerical values of addresses to ensure the correctness of access control measures.

\noindent
\textit{\underline{Flexible Interaction}.}
Addresses are also capable of being called upon and conducting arbitrary computations.
This attribute allows contracts to interact flexibly with other contracts, even if those contracts are deployed by external parties with undisclosed implementations.
Consequently, the ecosystem of smart contracts can evolve incrementally in a decentralized fashion, with various developers contributing via the deployment of their distinct contracts.
Subsequent developers can effortlessly interact with pre-existing contracts by invoking their functions using addresses.
Nevertheless, given the potential existence of adversarial actors creating and deploying their own contracts, thorough security checks must be enforce when invoking higher-order functions upon addresses.
